---
title: "Nielsen Relative Status Food Calories Analysis"
author: "Daniel O'Leary"
date: "2/17/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer
)
```

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

source(paste0(machine_path, "research/projects/niel/nielsen_analysis/relative_status_analysis/food_calories_regression_results_munge.R"))

res <-
  read_csv("D:/data/nielsen/tfp_calories_imputed_sc_by_household_quarterly/tfp_calories_imputed_sc_by_household_quarterly_regression_results.csv")
```



# Analysis

## Standardized betas for effect of relative income on percentage of calorie budget that goes to QFAHPD healthful categories


```{r}
models %>% 
  dplyr::select(
    key,
    income_demo_ranger_sar_scale
  ) %>% 
  ggplot(aes(fct_reorder(key, income_demo_ranger_sar_scale), income_demo_ranger_sar_scale)) +
  geom_col() + 
  #geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
  coord_flip()
```



### Label Insights calories raw

```{r}
qh_calories_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  filter(median_income_var %in% c("med_inc_niel_female_scale", "med_inc_niel_male_scale", "med_inc_gen_niel_scale", "median_income_county_scale")) %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo gen", "demo fem", "demo men", "county census"))) %>%
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>%
  ggplot(aes(year, estimate)) +
  geom_col() + 
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(id_controls ~ median_income_var)
```


### Label Insights calories servings conversion

```{r}
qh_calories_sc_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  filter(median_income_var %in% c("med_inc_niel_female_scale", "med_inc_niel_male_scale", "med_inc_gen_niel_scale", "median_income_county_scale")) %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo gen", "demo fem", "demo men", "county census"))) %>%
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>%
  ggplot(aes(year, estimate)) +
  geom_col() + 
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(id_controls ~ median_income_var)
```

### Label Insights calories raw imputed

```{r}
qh_calories_imputed_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  filter(median_income_var %in% c("med_inc_niel_female_scale", "med_inc_niel_male_scale", "med_inc_gen_niel_scale", "median_income_county_scale")) %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo gen", "demo fem", "demo men", "county census"))) %>%
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>%
  ggplot(aes(year, estimate)) +
  geom_col() + 
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(id_controls ~ median_income_var)
```


### Label Insights calories servings conversion imputed

```{r}
qh_calories_imputed_sc_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  filter(median_income_var %in% c("med_inc_niel_female_scale", "med_inc_niel_male_scale", "med_inc_gen_niel_scale", "median_income_county_scale")) %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo gen", "demo fem", "demo men", "county census"))) %>%
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>%
  ggplot(aes(year, estimate)) +
  geom_col() + 
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(id_controls ~ median_income_var)
```


## Median (across 2004 to 2017) standardized betas for regression models fit to TFP categories

### Median income computed county-level census data

#### Main effect controls model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "median_income_county_scale" & int == "no") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
  geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```


#### Interactive model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "median_income_county_scale" & int == "yes") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```


### Median income computed from demographics for women

#### Main effect controls model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_niel_female_scale" & int == "no") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```


#### Interactive model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_niel_female_scale" & int == "yes") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```


### Median income computed from demographics for men

#### Main effect controls model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_niel_male_scale" & int == "no") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```

#### Interactive model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_niel_male_scale" & int == "yes") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```


### Median income computed from demographics for women and men

#### Main effect controls model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_gen_niel_scale" & int == "no") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```

#### Interactive model

```{r}
res %>% 
  ungroup() %>% 
  filter(med_inc_var == "med_inc_gen_niel_scale" & int == "yes") %>% 
  dplyr::select(key, median_income_var_scale) %>% 
  group_by(key) %>% 
  summarise(
    median = median(median_income_var_scale, na.rm = TRUE)
  ) %>% 
  ggplot(aes(fct_reorder(key, median), median)) +
    geom_col() + labs(y = "median standardized beta", x = "tfp category") +
  coord_flip()
```
